### 2020-09-30 README.Rmd
a few more small updates

This folder contains folders with research journals.

@@

Contain materials from my earliest research journals relating to the LIME project. It is likely that the code in these files will not run. However, the knit versions of the R markdown documents may still be useful.

@@

The documents contained in the top folder are as follows:

>>>>

Contains folders with research journals:

@@

Contains materials from my earliest research journals relating to the LIME project. It is likely that the code in these files will not run. However, the knit versions of the R markdown documents may still be useful, so I included them in the repository.

@@

Files contained in the main folder of the repository:
